---
title: "Gus's Year in Books, 2022"
format: revealjs
editor: visual
---

```{r}
#| echo: FALSE
#| output: FALSE
data<-read_csv("goodreads_library_export.csv")%>%
  select()
names(data)<-str_replace_all(names(data), pattern = " ", replacement = "_" )

small_data<-data%>%
  select(Book_Id, Title, Author, My_Rating, Average_Rating, Number_of_Pages, Original_Publication_Year, Date_Read)
# small_data%>%
#   filter(is.na(Date_Read))%>%
#   select(Title, Date_Read)%>%
#   write_csv(file = "need_date_read.csv")
author_birth<-read_tsv("author_birth.tsv")
fixed_read<-read_csv("need_date_read.csv")
full_data<-full_join(small_data,fixed_read, by="Title")%>%
  mutate(Date_Read = case_when(is.na(Date_Read.x)~Date_Read.y,
                               TRUE~Date_Read.x))%>%
  left_join(author_birth)
```

## For the first time this year, I started tracking the books I read

- Slide one content

## And given my love of data visualization, I thought I'd give you a little closer look into my annual library

## Over this year I read 66 books

-

```{r}
full_data%>%
  arrange(Date_Read)%>%
  mutate(index = c(1:66))%>%
  ggplot(aes(x=Date_Read, y=index))+
  geom_point()+
  geom_path()+
  theme_classic()+
  labs(y="Total Books Read", y="Date") 
```

## 

## My books varied by length

Like stacked books?

## By age

Timeline?

## And by Geography

Map

## Usually my ratings matched others'

## But sometimes we REALLY disagreed
